Classless Java: Tuning Java Interfaces

### 2015-12-07 paper/sections/Translation.tex
formatting

\noindent\textbf{THEOREM }\Q!@ObjWeak!\\*
If a given interface table $\II$ IT is OK\\*
 where $\II$ has \Q!@ObjWeak!, 
$\valid(\C^{\II})$  and $\QM{of}\notin\dom(\C^{\II})$,\\*
then the interface table $[\![\II]\!]$ IT is OK.

\noindent\textbf{THEOREM }\Q!@Obj!\\*
If a given interface table $\II$ IT is OK\\*
 where $\II$ has \Q!@Obj!, 
$\valid(\C^{\II})$  and $\QM{of}\notin\dom(\C^{\II})$, and there is no heir of $\C^{\II}$,\\*
then the interface table $[\![\II]\!]$ IT is OK.
\bruno{The formatting of the theorems seems rather odd; why are the lines breaking?
Also naming the theorems after the annotations seems strange! Giving a proper name 
to the theorems seems a much better idea.}

>>>>

\noindent\textbf{THEOREM }\Q!@ObjWeak!\\*
If a given interface table $\II$ IT is OK 
 where $\II$ has \Q!@ObjWeak!, 
$\valid(\C^{\II})$  and $\QM{of}\notin\dom(\C^{\II})$,\\*
then the interface table $[\![\II]\!]$ IT is OK.

\noindent\textbf{THEOREM }\Q!@Obj! 
If a given interface table $\II$ IT is OK 
 where $\II$ has \Q!@Obj!, 
$\valid(\C^{\II})$  and $\QM{of}\notin\dom(\C^{\II})$, and there is no heir of $\C^{\II}$,\\*
then the interface table $[\![\II]\!]$ IT is OK.
\bruno{The formatting of the theorems seems rather odd; why are the lines breaking?
Also naming the theorems after the annotations seems strange! Giving a proper name 
to the theorems seems a much better idea.}
